The \dealii Library, Version 9.2

### 2020-05-28 9.2/paper.tex
Fix affiliations.

\author[3]{Timo~Heister}

\author[8]{Luca~Heltai}
\affil[8]{SISSA,
   International School for Advanced Studies,
   Via Bonomea 265,
   34136, Trieste, Italy.
   {\texttt{luca.heltai@sissa.it}}}

 \author[9]{Martin~Kronbichler}
 \affil[9]{Institute for Computational Mechanics,
   Technical University of Munich,
   Boltzmannstr.~15, 85748 Garching, Germany.
   {\texttt{kronbichler/munch@lnm.mw.tum.de}}}
%
% \author[10]{Ross~Maguire~Kynch}
% \affil[10]{Zienkiewicz Centre for Computational Engineering,
%   College of Engineering, Swansea University,
%   Bay Campus, Fabian Way, Swansea SA1 8EN, Wales, UK.
%   {\texttt{rkynch@gmail.com}}}
%
\author[11]{Matthias~Maier}
\affil[11]{Department of Mathematics,
  Texas A\&M University,
  3368 TAMU,
  College Station, TX 77845, USA.
  {\texttt{maier@math.tamu.edu}}}

  \author[9,13]{Peter Munch}

 \affil[13]{Institute of Materials Research, Materials Mechanics,
 Helmholtz-Zentrum Geesthacht,
 Max-Planck-Str. 1, 21502 Geesthacht, Germany.
   {\texttt{peter.muench@hzg.de}}}

%
% \author[4]{Jean-Paul~Pelteret}
%
 \author[14]{Reza Rastak}
 \affil[14]{Department of Civil and Environmental Engineering,
   Stanford University,
   Stanford, CA 94305, USA.
   {\texttt{rastak@stanford.edu}}}

@@

\author[14]{Zhuoran Wang}
\affil[14]{Department of Mathematics, Colorado State University, Fort Collins,
          CO 80523-1874, USA.
{\texttt{zhrwang@colostate.edu}}}         
\renewcommand{\labelitemi}{--}

>>>>

\author[4]{Timo~Heister}

\author[7]{Luca~Heltai}
\affil[7]{SISSA,
   International School for Advanced Studies,
   Via Bonomea 265,
   34136, Trieste, Italy.
   {\texttt{luca.heltai@sissa.it}}}

 \author[8]{Martin~Kronbichler}
 \affil[8]{Institute for Computational Mechanics,
   Technical University of Munich,
   Boltzmannstr.~15, 85748 Garching, Germany.
   {\texttt{kronbichler/munch@lnm.mw.tum.de}}}

\author[9]{Matthias~Maier}
\affil[9]{Department of Mathematics,
  Texas A\&M University,
  3368 TAMU,
  College Station, TX 77845, USA.
  {\texttt{maier@math.tamu.edu}}}

\author[8,10]{Peter Munch}
 \affil[10]{Institute of Materials Research, Materials Mechanics,
 Helmholtz-Zentrum Geesthacht,
 Max-Planck-Str. 1, 21502 Geesthacht, Germany.
   {\texttt{peter.muench@hzg.de}}}

%
% \author[4]{Jean-Paul~Pelteret}
%
 \author[11]{Reza Rastak}
 \affil[11]{Department of Civil and Environmental Engineering,
   Stanford University,
   Stanford, CA 94305, USA.
   {\texttt{rastak@stanford.edu}}}

@@

\author[13]{Zhuoran Wang}
\affil[13]{Department of Mathematics, Colorado State University, Fort Collins,
          CO 80523-1874, USA.
{\texttt{zhrwang@colostate.edu}}}         
\renewcommand{\labelitemi}{--}
